Recruits, abundance, and yield time series and contours

### 2023-11-04 recs-abund-yield-parameters.qmd
initial steps/prep results of simulations to create figs for manuscript.

nice_dispersal <- pretty_dispersal[stringr::str_detect(exp, valid_dispersal)]
nice_species <- pretty_species[stringr::str_detect(exp, valid_species)]
nice_noise <- pretty_noise[stringr::str_detect(exp, valid_noise)]

@@

### Experiment: `r params$experimenft`

>>>>

nice_dispersal <- pretty_dispersal[stringr::str_detect(exp, valid_dispersal)]
nice_species <- pretty_species[stringr::str_detect(exp, valid_species)]
nice_noise <- pretty_noise[stringr::str_detect(exp, valid_noise)]o

@@

### Experiment: `r params$experiment`
